---
title: "Credit Card"
author: "Henry Siegler"
date: "2022-11-25"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

```{r}
library(tidyverse)
library(here)
library(reshape2)
library(vtable)
```

```{r}
data <- read_csv(here("BankChurners.csv", "BankChurners.csv"))
```

```{r}
data <- data %>% 
  mutate(Exited = case_when(Attrition_Flag == "Existing Customer" ~ 0,
                              Attrition_Flag == "Attrited Customer" ~ 1),
         male = case_when(Gender == "M" ~ 1,
                          Gender == "F" ~ 0),
         ) %>% 
  select(-Naive_Bayes_Classifier_Attrition_Flag_Card_Category_Contacts_Count_12_mon_Dependent_count_Education_Level_Months_Inactive_12_mon_1,
         -Naive_Bayes_Classifier_Attrition_Flag_Card_Category_Contacts_Count_12_mon_Dependent_count_Education_Level_Months_Inactive_12_mon_2,
         -Gender,
         -Attrition_Flag,
         -CLIENTNUM)
```

### Descriptive Statistics
#### Response Variable is Total Transaction Count

```{r}
data %>% 
  select_if(is.numeric) %>% 
  st(out = "return")
```

```{r}
data %>% 
  select_if(is.numeric) %>% 
  cor() %>% 
  round(2) %>% 
  melt() %>% 
  ggplot(aes(Var1, Var2, fill = value)) + 
  geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
  theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 8, hjust = 1))+
 coord_fixed()
```
We can see from the correlation matrix that Avg_Open_To_Buy is highly correlated with Credit_Limit, so we will remove Avg_Open_To_Buy because it is redundant to keep it.

```{r}
cor(data$Avg_Open_To_Buy, data$Credit_Limit)
```
```{r}
data <- data %>% 
  select(-Avg_Open_To_Buy)
```



```{r}
cor_matrix <- cor(data %>% 
                    select_if(is.numeric)) %>% 
  round(2)

cor_matrix %>% 
  as.data.frame() %>% 
  select(Total_Trans_Ct) %>% 
  arrange(Total_Trans_Ct)
```

Now we will explore the Total_Trans_Ct variable and its relationship with other correlated variables in our data. 

```{r}
data %>% 
  ggplot(aes(x = Total_Trans_Ct)) + 
  geom_histogram()
```


```{r, fig.width = 5, fig.height = 10}
data %>% 
  ggplot(aes(x = Total_Trans_Ct)) + 
  geom_histogram() + 
  facet_wrap(~ Income_Category, ncol = 1)
```

For all of the income categories, we see a bimodal histogram for the Total_Trans_Ct. For people in the income category of less than $40K, we see that there is a larger spike in the second peak of the histogram compared to the other income categories.

```{r}
data %>% 
  ggplot(aes(x = Total_Trans_Ct)) + 
  geom_histogram() + 
  facet_wrap(~ Exited, nrow = 2)
```

We can see that the Total Transaction Counts for the customers who have have attrited has a unimodal distribution, with the center of the peak being significantly below where most of the Transaction Counts are for the customers who have not attrited. 

```{r}
data %>% 
  group_by(Total_Relationship_Count) %>% 
  summarise(mean(Total_Trans_Ct))

data %>% 
  ggplot(aes(x = as.factor(Total_Relationship_Count),
             y = Total_Trans_Ct)) + 
  geom_bar(stat = "summary",
           fun = mean,
           fill = "dodgerblue")
```


### Data Visualization

```{r}
data %>% 
  ggplot(aes(x = Total_Trans_Amt, y = Total_Trans_Ct, color = as.factor(Exited))) + 
  geom_point(alpha = 0.3) + 
  geom_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE)
```

### Splitting the Data


```{r}
set.seed(9)
data$id <- 1:nrow(data)

training_data <- data %>% 
  sample_frac(0.7)

test_data <- data %>% 
  anti_join(training_data, by = 'id')
```















